---
title: "p8105_hw5_xh2395"
author: "Xin  He"
date: "11/7/2019"
output: github_document
---

```{r setup, include=FALSE}
library(rvest)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "100%"
)
```

## Problem 1

```{r}
library(tidyverse)

set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

**The fuction**

```{r}
fill_missing = function(x) {
  
  if (!is.numeric(x)) {
    x[is.na(x)] = "virginica"
  }
  
  x[is.na(x)] = mean(x, na.rm = TRUE)
  
  x
  
}
```

**Apply the fuction**

```{r}
output = map_dfr(iris_with_missing, fill_missing)
```


## Problem 2

**Tidy the data**

```{r}
filename_df = list.files("./data")

study_df = tibble(
  filename= list.files("./data"),
  readin = str_c("./data/", filename_df)
)%>%
  mutate(
    week_obs = map(readin, read_csv),
    arm = substr(filename, 1, 3),
    subject_id=substr(filename, 5, 6),
    arm = replace(arm, arm == "con", "control"),
    arm = replace(arm, arm == "exp", "experiment"),
    subject_id=as.numeric(subject_id)
  ) %>% 
  unnest %>% 
  select(-filename, -readin) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    names_prefix = "week_",
    values_to = "observation"
  ) %>% 
  mutate(week = as.numeric(week))
```

**Spaghetti plot**

```{r}
study_df %>% 
  mutate(subject_id = as.character(subject_id)) %>% 
  ggplot(aes(x = week, y = observation, group = subject_id)) + 
  geom_line(aes(color = subject_id)) +
  facet_grid(. ~ arm)
```

In the experiment arm, the observation on each subject increase over time. Even though the increase is not steady, the overall trend is incresing.

However, in the control arm, the observation on each subject appears no increase over time. Even though the change is not steady, the overall trend shows no increase.


At 1st week, the observations in experiment arm are similar to the control arm. However, at 8th week, the observations in experiment arm are higher than the control arm.


## Problem 3

**The function**

```{r}
sim_regression = function(n, beta0 = 2, beta1 = 0) {
  
  sim_data = tibble(
    x = rnorm(n, mean = 0, sd = 1),
    y = beta0 + beta1 * x + rnorm(n, 0, 50)
  )
  
  fit = lm(y ~ x, data = sim_data)
    
  fit %>% 
     broom::tidy() %>% 
     filter(term == "x") %>% 
     select(estimate, p.value)
   
}
```

**Try when β1 = 0**

```{r}
sim_results = 
  rerun(10000, sim_regression(30, 2, 0)) %>% 
  bind_rows() %>% 
  rename(beta1_hat = estimate, p_value = p.value)
```

**Repeat for β1={1,2,3,4,5,6}**
   
```{r}
sim_results2 = 
  tibble(beta1_true = 1:6) %>% 
  mutate(
    output_lists = map(.x = beta1_true, ~rerun(10000, sim_regression(30, beta0 = 2, beta1= .x))),
    estimate_dfs = map(output_lists, bind_rows)) %>% 
  select(-output_lists) %>% 
  unnest(estimate_dfs) %>% 
  rename(beta1_hat = estimate, p_value = p.value)
```

**Plot for the association between effect size and power**

```{r}
sim_results2 %>% 
  filter(p_value < 0.05) %>% 
  group_by(beta1_true) %>%
  summarize(n = n()) %>% 
  mutate(power = n / 10000) %>% 
  ggplot(aes(x = beta1_true, y = power)) + 
  geom_point() +
  geom_line() +
  scale_x_continuous(breaks = seq(0, 6, 1)) +
  labs(title = "The association between effect size and power")
```

According to the plot, we find that the power goes higher when the effect size goes higher. There is a positive association between effect size and power.

**Plot for average estimate of β̂1 and the true value of β1**

```{r}
sim_results2 %>% 
  group_by(beta1_true) %>%
  summarize(average_estimate = mean(beta1_hat)) %>% 
  ggplot(aes(x = beta1_true, y = average_estimate)) + 
  geom_point() +
  geom_line() +
  scale_x_continuous(breaks = seq(0, 6, 1)) +
  scale_y_continuous(breaks = seq(0, 7, 1)) +
  labs(title = "The association between average estimate of β̂1 and the true value of β")
```

**only in samples for which the null was rejected**

```{r}
sim_results2 %>% 
  filter(p_value < 0.05) %>% 
  group_by(beta1_true) %>%
  summarize(average_estimate = mean(beta1_hat)) %>% 
  ggplot(aes(x = beta1_true, y = average_estimate)) + 
  geom_point() +
  geom_line() +
  scale_x_continuous(breaks = seq(0, 6, 1)) +
  labs(title = "The association between average β̂1 and β1 only when null was rejected")
```

According to the plot, the sample average of β̂1 across tests for which the null is rejected is not approximately equal to the true value of β1.
Because the null hypothesis is that the estimated β̂1 is equal to the true β1.If we use data only in samples for which the null was rejected, there is no doubt that estimated β̂1 is different from the true β.









